### 2016-03-14 paper/stereo.tex
minor changes
Hang

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms highly informative
in most stereo problems.  Our experiments have also supported this,
where the fusion method (i.e., the use of proposal generation) rather
makes it slow due to the overhead.
%\hang{Don't quite understand this sentence. Does the ``dominant'' means
%running time or energy? In my experiments, unary terms are pre-computed
%and are not counted into the running time}
Therefore, we have chosen single thread Alpha Expansion(AE), Parallel
Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical
Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
with graph-cuts optimization as the competing methods.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
4. In this case one thread will fuse 4 labels by TRW-S per iteration and
never exchanges solutions with other threads. SF-MF implies
$\alpha+\beta=1$, where each thread will expand 3 labels (repeat
$\alpha=1, \beta=0$ for 3 iterations) and then fuse one solution from
other threads ($\alpha=0, \beta=1$) by QPBO. In the later case, a thread
randomly chooses one target thread to copy a solution. For standard SF,
we have used ($\alpha=4, \beta=1$). For the SF-SS architecture, we
perform a multi-way fusion at the end to fuse solutions from all the threads.

%
%
%
%
To make the comparison simple, we restrict our proposal generator
in each thread to only generate constant-label proposals within a
subset of all labels. Graph-cuts is used in fusing a constant-label
proposal as the energy is submodular. QPBO is used in fusing a
different solution from another thread as the energy is
non-submodular in general.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\noindent For simple stereo problems as ours, the sophistication of
photometric consistency function~\cite{mvs_furukawa_survey} makes
unary terms highly informative, thus eliminates the necessity of
adopting sophicticated proposals. Our experiments have also supported
this, where the fusion method (i.e., the use of proposal generation)
rather makes it slow due to the overhead, while not improving final
energy. Therefore, we have chosen algorithms based on Alpha Expansion,
namely single thread Alpha Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion}
for competing methods. For HF, we use Alpha Expansion when either of
the child node is leaf node (constant label) and QPBO for all other
nodes.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-MF (SF without multi-way fusion), SF-SS (SF without
solution sharing), and the standard SF.
%
SF-MF implies $\alpha+\beta=1$, where each thread will expand 4 labels
(repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha Expansion and
then fuse one solution from other threads ($\alpha=0, \beta=1$) by
QPBO. In the later case, a thread randomly chooses one target thread
to take its solution for fusion. SF-SS implies $\beta=0$, where
$\alpha$ is the free parameter and set to 4. In this case one thread
will fuse 4 labels, together with current solution by TRW-S per
iteration and never exchanges solutions with other threads. We perform
a multi-way fusion at the end to fuse solutions from all the threads
(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).

%
%
%
%
To make the comparison simple, we restrict our proposal generator
in each thread to only generate constant-label proposals within a
subset of all labels.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
